General constraints on magic distillation protocols from statistical mechanics

### 2021-04-20 appendix.tex
a few more changes

\begin{lemma} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. Let $a > 0$ and $b \in \mathbb{R}$ then $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$.
\end{lemma}\label{lemma:Lorenz_linearity}
\begin{proof} The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order. However since $a > 0$, this is the same permutation that puts  $(p_i/r_i)$ in non-increasing order. We thus have
\begin{equation}
(\sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)}) = (\sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)}) \nonumber,
\end{equation}
therefore the value of the Lorenz function at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
\begin{equation}
L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b x_k,
\end{equation}
and so from linearity, we have in general $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any intermediate $x$.
\end{proof}
\subsection{Embedding map}

>>>>

\begin{lemma} Let $\p$ be a quasi-probability distribution and let $\r$ be a probability distribution with strictly non-zero components. Let $a > 0$ and $b \in \mathbb{R}$ then $L_{a\p + b \r | \r} (x) = a L_{\p |\r}(x) + b x$.
\end{lemma}\label{lemma:Lorenz_linearity}
\begin{proof} The Lorenz curve of $a\p + b \r$ relative to $\r$ passes through $(0,0)$ and the points $(\sum_{i=1}^k{r_{\pi(i)}}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)})$ where $\pi$ is the permutation that puts $(a p_i/r_i + b)$ in non-increasing order. Since $a > 0$, the permutation $\pi$ puts  $(p_i/r_i)$ in non-increasing order too. We thus have
\begin{align*}
&\left( \sum_{i=1}^kr_{\pi(i)}, \sum_{i=1}^k(a \p + b \r)_{\pi(i)} \right) = \\ 
&\left( \sum_{i=1}^k r_{\pi(i)},a \sum_{i=1}^k  p_{\pi(i)} + b\sum_{i=1}^k r_{\pi(i)} \right) \nonumber,
\end{align*}
therefore the value of the Lorenz function at each potential elbow point $x_k = \sum_{i=1} ^kr_{\pi(i)}$ is given by
\begin{align}
&L_{a \p +b \r|\r} (x_k) = a L_{\p|\r} (x_k) + b L_{\r|\r}(x_k) = \nonumber\\
&a L_{\p|\r} (x_k) + b x_k,
\end{align}
so we have $L_{a\p  + b\r|\r} (x) = a L_{\p |\r}(x) + b x$ for any $x \in [0,1]$ due to linearity.
\end{proof}
\subsection{Embedding map}

### 2021-04-20 magic_paper.tex
a few more changes

\begin{figure}[t]
    \centering
        \includegraphics[scale=0.3
        ]{figs/operations.pdf}
    \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) are labelled, with other established magic theories also contained within the yellow regions.
    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
    Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
    Within each $\sigma$--fragment, relative majorisation can be used allowing for a tractable approach towards the study of magic state interconversions.
    }
    \label{fig:zoo}
\end{figure}

@@

At this point we note that, to our knowledge, this application of majorization to quasi-distributions in  physics has not been considered previously. The caveat here is that relative majorization ranges over stochastic maps that obey a fixed transformation ($A\r = \r'$), while in the case of the Wigner representation there is an additional restriction that the symplectic structure of the phase space is respected. Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions in the fragment. This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics? We shall \nick{return} to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.

>>>>

\begin{figure}[t]
    \centering
        \includegraphics[scale=0.3
        ]{figs/operations.pdf}
    \caption{\textbf{Decomposition of a magic theory $\R$ into $\sigma$--fragments.} 
	Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) are labelled, with other established magic theories also contained within the yellow regions.
    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$. 
    Each $\O_\sigma$ is extensible to a set of stochastic maps outside the $\cptp$ operations.
    Within each $\sigma$--fragment, relative majorisation can be used allowing for a tractable approach towards the study of magic state interconversions.
    }
    \label{fig:zoo}
\end{figure}

@@

At this point we note that, to our knowledge, this application of majorization to quasi-distributions in  physics has not been considered previously. The caveat here is that relative majorization ranges over stochastic maps that obey a fixed transformation ($A\r = \r'$), while in the case of the Wigner representation there is a stronger restriction that the symplectic structure of the phase space is respected. Therefore, any majorization constraint can provide necessary, but not sufficient conditions on magic state interconversions. This observation raises a question that to our knowledge has not been previously considered in the classical statistical mechanics literature: what are the conditions for symplectic majorization of classical statistical mechanics? We shall \nick{return} to this question later on when we discuss how our approach could be used to construct concrete lower-bounds on distillation rates in~\cref{sec:lower_bounds}.
